PM Mungbean meta-analysis

### 2020-12-20 02_Preliminary_analysis.Rmd
Examine the output of a stacked bar graph

```{r YieldGain_plot}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   group_by(trial_ref, location, year)%>%
   summarise(yield_gain_m = mean(yield_gain),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             .groups = "drop")%>%
   mutate(trial = paste(location,year,sep = "\n"))%>%
   ggplot(aes(reorder(trial, yield_gain_m), yield_gain_m))+
   geom_bar(stat = "identity")+
   geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
                     ymin = yield_gain_m - yield_gain_se))+
   theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

```{r tebuAndPropi_dose}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   select(
      trial_ref,
      year,
      location,
      first_sign_disease,
      fungicide_ai,
      dose_ai.ha,
      total_fungicide
   ) %>%
   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole\nor propiconazole dose") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq()
```

>>>>

```{r YieldGain_plot}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole"|
             fungicide_ai == "control")%>%
   mutate(spray_NoSpray = factor(ifelse(fungicide_ai == "control","control","Fungicide treated"))) %>%
   mutate(control_yield = ifelse(fungicide_ai == "control",grain_yield.t.ha.,NA))%>%
   group_by(trial_ref, location, year,spray_NoSpray)%>%
   summarise(yield_c = mean(control_yield),
             yield_gain_m = mean(yield_gain, na.rm = TRUE),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             .groups = "drop")%>%
   mutate(trial = paste(location,year,sep = "\n"))%>%
   mutate(yield = ifelse(spray_NoSpray == "control", yield_c, yield_gain_m))%>%
   ggplot(aes(reorder(trial_ref, yield), yield, fill = (spray_NoSpray)))+
   geom_col()+
   # geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
   #                   ymin = yield_gain_m - yield_gain_se))+
   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   scale_fill_usq() +
   scale_colour_usq()

@@

```{r tebuAndPropi_dose}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole\nor propiconazole dose") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq()
```
